% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Brenda Baud} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document} 
\thispagestyle{empty} % this page does not have a header
\name{Zheng Liu}
\address{120 Chester Road\\
Eight Mile Plains\\
0434130283}


\begin{resume}
\vspace{0.1in}
\moveleft.5\sectionwidth\centerline{Objective: Position as technical writer or editor.}  

\section{EDUCATION}
\vspace{0.1in} 
 
    ITEE, University of Queensland, QLD, Australia, Ph.D.,
    Computer Science, 2005
    
    Institute of Computer Science, Jilin University, Jilin, China, Bc.S.,
    Computer Science, 1999
 
\section{SKILLS} 
\vspace{0.1in}
  {\bf C/C++ Programming}
    \begin{itemize} % Use \item[] to prevent a bullet from appearing
      \item[] Academic papers, technical reports, functional documents, 
        newsletters, nonfiction articles. Published papers on 
        technical writing, research in organizational writing. 
        Wrote computer documentation, including CAD/CAM, PC and 
        interface material. Produced technical papers on history 
        of technology; revised tables of contents, reference 
        material. 
      \end{itemize}
  {\bf Quality Engineering} 
       \begin{itemize}
        \item[] Taught editorial writing courses; trained in editing 
        techniques (Garrison Institute of Writing); edited 
        research proposals, promotional material, newsletters.
    \end{itemize}

  {\bf Consulting and Customer Caring} 
        \begin{itemize}
        \item[] Taught technical writing, business writing, upper 
        division writing courses for engineering, computer 
        science, management students. Trained teachers in 
        graduate-level writing course. Led professional 
        development workshops in business writing to college 
        administrators. Supervised teaching assistants; 
        coordinated tutoring network for academic support 
        services. 
       \end{itemize}

   {\bf  Research} 
        \begin{itemize}
        \item[]  Investigated use of word processors as primary writing 
        implements in organizational settings. Developed 
        usability instrument for assessing computer 
        documentation; researched use of icons in interfaces. 
        Consulted in use of field methods for organizational 
        analysis. Provided writing consultations for graduate 
        research projects. Training in statistical methods in 
        communications research, introductory course, RPI. 
        Training in field research techniques, SUNY. 
       \end{itemize} 

   {\bf Hardware Interface Development} 
        \begin{itemize}
        \item[] Courses: Basic, Pascal. Types and Programs: IBM 
        Mainframe/3081D (MTS: Textform, SPSSX; IBM MINI/360 
        (GML/SCRIPT, CAD/CAM); IBM PC (Multimate, Wordperfect); 
        Apple II-Plus (Macwrite, Pagemaker). 
        \end{itemize}
 
\section{EMPLOYMENT} 
\vspace{0.1in} 
    {\bf System Engineer, QA Engineer,} Nokia Qt Software, Brisbane, Australia
    2006 - 2012
 
    {\bf Programmer, Support Engineer,} Nokia Qt Software, Brisbane, Australia
    2006 - 2012
 
    {\bf Self Employeed,} VRCATS Software, Brisbane, Australia
    2005 - 2006
 
    {\bf Teaching Assistant,} ITEE, University of Queensland, Brisbane, Australia 
    2001 - 2005 
 
    {\bf System Administrator,} Jilin Paradise International Trading Limited, Jilin, China
    2000 - 2000
 
    {\bf Software Engineer, Team Leader,} JLU Zhengyuan Information Technology Limited, Beijing, China
    1999 - 2000
 
 
\section{PROFESSIONAL AFFILIATIONS} 
\vspace{0.1in} 
    Society of Technical Communication \\
    Association of Business Communication \\
    Modern Language Association \\
    National Council of Teachers of English \\
    Conference on College Composition and Communication \\
    Society of Professional Writing Consultants 

\section{PUBLICATIONS} 
\vspace{0.1in}
``Playing to Win,'' {\it Hers, The New York Times Magazine, July 3, 1988} 

 
``Analyzing Corporate Communications Policies using Ethnographic 
Methods,'' {\it The Proceedings of the Conference on Corporate 
Communications}, Fairleigh Dickinson University, Madison, NJ, May 
1988. 
 
``Toward a Cognitive Theory of Visual Processing,'' {\it The Proceedings 
of the ITCC, Society of Technical Communication}, Philadelphia, 
PA, May 1988. 
 
``Organizational, Interpersonal and Technological Influences on 
Newspaper Writing, An Ethnographic Study,'' In review. 
 
``Combining Elegance and Readability: Walker Gibson's Tough, Sweet 
and Stuffy,'' {\it IEEE Transactions in Professional Communication}, 
December 1987. 
 
``Walker Gibson's Tough Sweet and Stuffy: A Workshop in Style for 
Engineers,'' {\it Linking Technology and Users: Conference Record of 
the IPCC}, October 1986. 
 
``That Damn Ram: Hydraulic Power at Chesterwood, 1908-1932,'' 
Unpublished paper for Chesterwood and the Society for Historic 
Preservation, 1984. 
 
``Sculpture Media,'' Unpublished paper for Chesterwood and the 
Society of Historical Preservation, 1984. 
 
{\it The Chesterwood Pedestal}, Volume 3, 1985, Newsletter of The 
Society of Historical Preservation, Chesterwood, Stockbridge, MA. 
 
\end{resume}
\end{document}






























